---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# pseR

Pull and analyse PSE data. Currently limited only to Investagrams as source which is limited to past year data only.

## Installation

Install devtools to easily install `pseR`. 

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("nfrimando/pseR")
```

## Examples

Extract historical PSE data with `pull_pse_data()`

```{r message = FALSE, warning = FALSE}
suppressPackageStartupMessages({library(pseR); library(dplyr)}) 
stock.dt <- pull_pse_data(c("JFC", "MBT", "FGEN","BPI", "URC",
                            "ALI", "MER", "ABS", "GLO"))
stock.dt %>% head()
```

## Analytics using `tidyquant`

The package [`tidyquant`](https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ04-charting-with-tidyquant.html) has convenient functions that allows easy implementation for visualisation and analysis.

```{r}
suppressPackageStartupMessages({library(tidyquant); library(ggplot2)})
stock.dt %>%
  ggplot(aes(x = as.Date(date), y = close)) +
  geom_barchart(aes(open = open, high = high, low = low, close = close)) +
  labs(title = "PSE Stocks Daily Past 1 Year", y = "Closing Price", x = "") + 
  facet_wrap(~code, scales = "free") + 
  scale_x_date(date_breaks = "3 months", date_labels = "%b %d") + 
  theme_tq()
```

