---
title: "Support and Resistance"
author: "Nigel Rimando"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(pseR) # devtools::install_github("nfrimando/pseR")
library(tidyquant)
library(ggplot2)
library(tidyverse)
library(glue)
library(magrittr)
library(gt)
```

# Purpose

This report outlines companies with their support and resistance bands scraped from [Investagram](https://www.investagrams.com/Home/).

DO NOT MAKE THESE MISTAKES: https://www.youtube.com/watch?v=IbEQiCGgKcE

* The more times SR is tested within a short period of time, the weaker it becomes
* Don't set your stops just below support (or resistance)
* Don't buy chop move into support (avoid many mini resistance or support levels)
* Don't treat SR as lines -- treat them as ares

# Summary Data {.tabset}

```{r}
days_look_back <- 90
stock_code_info.dt <- 
  # Blue Chips
  data.frame(
    codes = c("AC", "AEV", "AGI", "ALI", "AP", "BDO", "BPI", "DMC", "FGEN", "GLO",
              "GTCAP", "ICT", "JFC", "JGS", "LTG", "MBT", "MEG", "MER", "MPI", "PCOR",
              "PGOLD", "RLC", "RRHI", "SCC", "SECB", "SM", "SMC", "SMPH", "TEL", "URC"),
    class = rep("Blue Chip", 30)
  ) %>% 
  # Alternative
  rbind(
    data.frame(
      codes = c("AXLM", "FRUIT", "DNL", "WLCON", "HOME", "EEI", "MAC", "MWIDE",
                "ACEPH", "FB", "SSI", "BLOOM", "NOW", "MAXS", "PIZZA", 
                "FMETF"),
      class = rep("Alternative", 16)
    )
  ) %>% 
  # Concept Play
  rbind(
    data.frame(
      codes = c("IMI", "DITO", "TECH", "NIKL", "PXP", "ALLHC", "IDC"),
      class = rep("Concept Play", 7)
    )
  ) %>% 
  # Mark In Portfolio
  mutate(
    in_portfolio = codes %in% c("FMETF", "AGI", "ALI", "BPI", "FGEN", "LTG", "MER", "PIZZA", "URC", "EEI")
  )

top_codes <- 30

stocks.dt <- scrape_investagram(as.character(stock_code_info.dt$codes)) %>% 
  map_df(
    function(x) {
      last_close <- (x$data %>% arrange(desc(date)))$close[1]

      x$data %>% 
        mutate(
          support_1 = x$bands$support_1,
          support_2 = x$bands$support_2,
          resist_1 = x$bands$resist_1,
          resist_2 = x$bands$resist_2
        ) %>% 
        filter(date >= Sys.Date() - days_look_back) %>% 
        mutate(last_close = last_close)
    },
    .id = "code"
  )
```

```{r message = FALSE, warning = FALSE}
# Create Summary Table
summary.dt <- stocks.dt %>% 
  group_by(code) %>% arrange(desc(date)) %>% 
  filter(row_number() == 1) %>% 
  mutate(perc_diff_support_1 = (last_close - support_1)/last_close) %>% 
  mutate(perc_diff_support_2 = (last_close - support_2)/last_close) %>% 
  mutate(perc_diff_resist_1 = (last_close - resist_1)/last_close) %>% 
  mutate(perc_diff_resist_2 = (last_close - resist_2)/last_close) %>% 
  mutate(potential_gain = (resist_1 - last_close)/last_close) %>% 
  mutate(potential_loss = -(last_close - support_1)/last_close) %>%
  mutate(potential_gain_2 = (resist_2 - last_close)/last_close) %>% 
  mutate(potential_loss_2 = -(last_close - support_2)/last_close) %>%
  ungroup() %>% 
  inner_join(stock_code_info.dt, by = c("code" = "codes")) %>% 
  select(code, class, in_portfolio, close, support_1, resist_1, 
         perc_diff_support_1, perc_diff_support_2,
         perc_diff_resist_1, perc_diff_resist_2, 
         support_2, resist_2,
         potential_gain, potential_loss,
         potential_gain_2, potential_loss_2) %>% 
  ungroup()
```

* close - last closing price as of report run
* perc_diff_ - difference based on last close price (denominator is close price)

$$ \text{Percent Difference} = \frac{\text{Closing Price} - \text{Price of Interest}}{\text{Closing Price}} $$

## Close to Support (Buy Signal)

* potential_gain - if i buy now, the % gain if I hit resistance
* potential_loss_2 - if i buy now, the % loss if we breach support 1 and reach support 2

```{r message = FALSE, warning = FALSE}
summary.dt %>%
  arrange(perc_diff_support_1) %T>% 
  {dt <- .; buy_signals.dt <<- dt %>% head(top_codes)} %>% 
  select(code, class, in_portfolio, close, support_1, support_2, perc_diff_support_1, perc_diff_support_2,
         potential_gain, potential_loss_2, resist_1, resist_2) %>% 
  gt() %>% 
  tab_header(
    title = "Prices Closest to Support",
    subtitle = glue("As of {Sys.Date()}")
  ) %>% 
  fmt_currency(
    columns = vars(close, support_1, support_2),
    currency = "PHP"
  ) %>% 
  fmt_percent(
    columns = vars(perc_diff_support_1, perc_diff_support_2, potential_gain, potential_loss_2)
  ) %>% 
  data_color(
    columns = vars(perc_diff_support_1, perc_diff_support_2),
    colors = scales::col_numeric(
      palette = c("green", "yellow", "red"),
      domain = NULL
    )
  ) %>% 
  tab_style(
    style = cell_fill(color = "lightblue"),
    locations = cells_body(
      columns = vars(in_portfolio),
      rows = in_portfolio
    )
  ) %>% 
  tab_style(
    style = cell_fill(color = "lightyellow"),
    locations = cells_body(
      columns = vars(in_portfolio),
      rows = !in_portfolio
    )
  ) %>% 
  tab_style(
    style = cell_fill(color = "lightgreen"),
    locations = cells_body(
      columns = vars(class),
      rows = class == "Blue Chip"
    )
  ) 
  
```

## Close to Resistance (Sell Signal)

* potential_loss - if I don't sell now, the % I would lose if hit support
* potential_gain_2 - if I sell now, the % I would have gotten if I chose to hold

```{r}
summary.dt %>%
  arrange(desc(perc_diff_resist_1)) %T>% 
  {dt <- .; sell_signals.dt <<- dt %>% head(top_codes)} %>%
  select(code, class, in_portfolio, close, resist_1, resist_2, perc_diff_resist_1, perc_diff_resist_2,
         potential_loss, potential_gain_2, resist_1, resist_2) %>% 
  gt() %>% 
  tab_header(
    title = "Prices Closest to Resist",
    subtitle = glue("As of {Sys.Date()}")
  ) %>% 
  fmt_currency(
    columns = vars(close, resist_1, resist_2),
    currency = "PHP"
  ) %>% 
  fmt_percent(
    columns = vars(perc_diff_resist_1, perc_diff_resist_2, potential_loss, potential_gain_2)
  ) %>% 
  data_color(
    columns = vars(perc_diff_resist_1, perc_diff_resist_2),
    colors = scales::col_numeric(
      palette = rev(c("green", "yellow", "red")),
      domain = NULL
    )
  ) %>% 
  tab_style(
    style = cell_fill(color = "lightblue"),
    locations = cells_body(
      columns = vars(in_portfolio),
      rows = in_portfolio
    )
  ) %>% 
  tab_style(
    style = cell_fill(color = "lightyellow"),
    locations = cells_body(
      columns = vars(in_portfolio),
      rows = !in_portfolio
    )
  ) %>% 
  tab_style(
    style = cell_fill(color = "lightgreen"),
    locations = cells_body(
      columns = vars(class),
      rows = class == "Blue Chip"
    )
  ) 
```

#

-------------

# Charts

## Top `r top_codes` Close to Support {.tabset}

```{r results = 'asis', fig.width = 10}

cat("\n")

codes <- factor(buy_signals.dt$code, levels = buy_signals.dt$code)

for (i in codes) {
  cat(glue("### {i} \n\n"))
  
  plot <- stocks.dt %>%
    filter(code == !!i) %>%
    arrange(date) %>% mutate(latest_close_price = tail(close, 1)) %>% 
    mutate(potential_gain = (resist_1 - last_close)/last_close) %>% 
    mutate(potential_loss = (last_close - support_1)/last_close) %>% 
    mutate(potential_gain_2 = (resist_2 - last_close)/last_close) %>% 
    mutate(potential_loss_2 = (last_close - support_2)/last_close) %>%
    ggplot(aes(x = as.Date(date), y = close)) +
    geom_barchart(aes(open = open, high = high, low = low, close = close)) +
    labs(title = glue("{i} Daily Past {days_look_back} Days with Bands"), y = "Price", x = "") +
    facet_wrap(~code, scales = "free", ncol = 2) +
    scale_x_date(date_breaks = "3 months", date_labels = "%b %d") +
    theme_tq() +
    theme(plot.title = element_text(hjust = 0.5)) +
    geom_text(mapping = aes(x = Sys.Date() + 3, y = last_close, label = last_close, vjust = 0), color = "blue") +
    geom_hline(mapping = aes(yintercept = support_1), linetype = "dashed", color = "blue") +
    geom_text(mapping = aes(x = Sys.Date() + 3, y = support_1, 
                            label = glue("{support_1} ({round(potential_loss*100,2)})%"), vjust = 1),
              color = "red") +
    geom_hline(mapping = aes(yintercept = support_2), linetype = "dotted", color = "blue") +
    geom_text(mapping = aes(x = Sys.Date() + 3, y = support_2, 
                            label = glue("{support_2} ({round(potential_loss_2*100,2)})%"), vjust = 1), 
              color = "red") +
    geom_hline(mapping = aes(yintercept = resist_1), linetype = "dashed", color = "red") +
    geom_text(mapping = aes(x = Sys.Date() + 3, y = resist_1, 
                            label = glue("{resist_1} ({round(potential_gain*100,2)})%"), vjust = -1),
              color = "green") +
    geom_hline(mapping = aes(yintercept = resist_2), linetype = "dotted", color = "red") +
    geom_text(mapping = aes(x = Sys.Date() + 3, y = resist_2, 
                            label = glue("{resist_2} ({round(potential_gain_2*100,2)})%"), vjust = -1), 
              color = "green")
  
  print(plot)
  
  cat("\n\n")
}

```

##

## Top `r top_codes` Close to Resistance {.tabset}

```{r results = 'asis', fig.width = 10}

cat("\n")

codes <- factor(sell_signals.dt$code, levels = sell_signals.dt$code)

for (i in codes) {
  cat(glue("### {i} \n\n"))
  
  plot <- stocks.dt %>%
    filter(code == !!i) %>%
    arrange(date) %>% mutate(latest_close_price = tail(close, 1)) %>% 
    mutate(potential_gain = (resist_1 - last_close)/last_close) %>% 
    mutate(potential_loss = (last_close - support_1)/last_close) %>% 
    mutate(potential_gain_2 = (resist_2 - last_close)/last_close) %>% 
    mutate(potential_loss_2 = (last_close - support_2)/last_close) %>%
    ggplot(aes(x = as.Date(date), y = close)) +
    geom_barchart(aes(open = open, high = high, low = low, close = close)) +
    labs(title = glue("{i} Daily Past {days_look_back} Days with Bands"), y = "Price", x = "") +
    facet_wrap(~code, scales = "free", ncol = 2) +
    scale_x_date(date_breaks = "3 months", date_labels = "%b %d") +
    theme_tq() +
    theme(plot.title = element_text(hjust = 0.5)) +
    geom_text(mapping = aes(x = Sys.Date() + 3, y = last_close, label = last_close, vjust = 0), color = "blue") +
    geom_hline(mapping = aes(yintercept = support_1), linetype = "dashed", color = "blue") +
    geom_text(mapping = aes(x = Sys.Date() + 3, y = support_1, 
                            label = glue("{support_1} ({round(potential_loss*100,2)})%"), vjust = 1),
              color = "red") +
    geom_hline(mapping = aes(yintercept = support_2), linetype = "dotted", color = "blue") +
    geom_text(mapping = aes(x = Sys.Date() + 3, y = support_2, 
                            label = glue("{support_2} ({round(potential_loss_2*100,2)})%"), vjust = 1), 
              color = "red") +
    geom_hline(mapping = aes(yintercept = resist_1), linetype = "dashed", color = "red") +
    geom_text(mapping = aes(x = Sys.Date() + 3, y = resist_1, 
                            label = glue("{resist_1} ({round(potential_gain*100,2)})%"), vjust = -1),
              color = "green") +
    geom_hline(mapping = aes(yintercept = resist_2), linetype = "dotted", color = "red") +
    geom_text(mapping = aes(x = Sys.Date() + 3, y = resist_2, 
                            label = glue("{resist_2} ({round(potential_gain_2*100,2)})%"), vjust = -1), 
              color = "green")
  
  print(plot)
  
  cat("\n\n")
}

```

##
